---
title: "Assignment 6 — Testing & Documentation Demo"
subtitle: "Fengping River Hydropower Project — 3 functions, tests, docs, examples"
author: "[MAYA SCANLON , WILLIAM LIEN]"
date: today
format:
  html:
    toc: true
    toc-depth: 2
    embed-resources: true
editor: source
execute:
  echo: true
  warning: false
  message: false
---

# Purpose of this file

This file is a **short, standalone demo** for Assignment 6. It does NOT run
the full project report (`fp_hydro_main.qmd`, which takes several minutes) —
it focuses on exactly **3 functions** and shows, for each one:

1. Its **roxygen2 documentation** (description, `@param`, `@return`) —
   pulled directly from the source file.
2. Its **unit tests** (`testthat`, `expect_*`), run live from
   `tests/test_<function_name>.R`, with a PASS/FAIL summary printed below.
3. A **worked example** showing the function used on real or representative
   data.

| # | Function | Module | Test file | What it checks |
|---|---|---|---|---|
| 1 | `fill_daily_na()` | `module/hydro_reservoir.R` | `tests/test_fill_daily_na.R` | Daily streamflow format/cleaning — catches bad input (missing columns, bad method, negative flows) |
| 2 | `estimate_daily_ssl()` | `module/hydro_sediment.R` | `tests/test_estimate_daily_ssl.R` | Matches the sediment rating curve (fit from sparse sampling data) to the continuous daily flow record |
| 3 | `compute_npv()` | `module/hydro_finance.R` | `tests/test_compute_npv.R` | NPV from a cash-flow vector, where `cash_flows[1]` is the CAPEX-driven year-0 outflow |

```{r setup}
library(tidyverse)
library(here)
library(testthat)

source(here("module", "hydro_reservoir.R"))
source(here("module", "hydro_sediment.R"))
source(here("module", "hydro_finance.R"))

# Helper: pull the contiguous block of roxygen ("#'") comment lines that
# sits directly above a function definition, and print it as plain text.
show_roxygen_doc <- function(module_file, fn_name) {

  src   <- readLines(here("module", module_file))
  def_i <- grep(sprintf("^%s\\s*<-\\s*function", fn_name), src)[1]

  stopifnot(!is.na(def_i))

  start_i <- def_i - 1L
  while (start_i >= 1L && grepl("^#'", src[start_i])) start_i <- start_i - 1L
  start_i <- start_i + 1L

  doc_lines <- src[start_i:(def_i - 1L)]
  cat(paste(sub("^#'\\s?", "", doc_lines), collapse = "\n"))
}
```

# 1. `fill_daily_na()` — daily flow data format

## Documentation

```{r doc-fill-daily-na}
show_roxygen_doc("hydro_reservoir.R", "fill_daily_na")
```

## Tests (`tests/test_fill_daily_na.R`)

```{r test-fill-daily-na}
test_file(here("tests", "test_fill_daily_na.R"))
```

## Example use

```{r ex-fill-daily-na}
synth <- data.frame(
  date  = seq(as.Date("2020-01-01"), as.Date("2020-01-10"), by = "day"),
  Q_cms = c(5, 5.2, NA, NA, 5.6, 5.8, 6.0, NA, 6.2, 6.4)
)

filled <- fill_daily_na(synth, method = "linear")
filled
```

# 2. `estimate_daily_ssl()` — sediment-to-flow matching

## Documentation

```{r doc-estimate-daily-ssl}
show_roxygen_doc("hydro_sediment.R", "estimate_daily_ssl")
```

## Tests (`tests/test_estimate_daily_ssl.R`)

```{r test-estimate-daily-ssl}
test_file(here("tests", "test_estimate_daily_ssl.R"))
```

## Example use

We fit the rating curve on a small synthetic sediment-sampling dataset
(representing the sparse field samples), then apply it to a daily flow
series (representing the continuous gauge record) to get a matched daily
sediment-load estimate.

```{r ex-estimate-daily-ssl}
set.seed(1)
n   <- 30
Q   <- runif(n, min = 5, max = 200)
SSL <- 10 * Q^1.6 * exp(rnorm(n, 0, 0.3))

sed_sample <- data.frame(
  Discharge_CMS  = Q,
  Sus_Load_MTDay = SSL,
  flag           = "ok"
)

rating_curve <- fit_rating_curve(sed_sample, plot_fit = FALSE)

daily_flow <- data.frame(
  date  = seq(as.Date("2020-01-01"), by = "day", length.out = 10),
  Q_cms = c(2, 3, 8, 15, 30, 60, 40, 20, 6, 4)
)

daily_ssl <- estimate_daily_ssl(daily_flow, rating_curve, Q_min_transport = 5.0)
daily_ssl
```

# 3. `compute_npv()` — NPV / CAPEX

## Documentation

```{r doc-compute-npv}
show_roxygen_doc("hydro_finance.R", "compute_npv")
```

## Tests (`tests/test_compute_npv.R`)

```{r test-compute-npv}
test_file(here("tests", "test_compute_npv.R"))
```

## Example use

A simple scenario: CAPEX of NTD 1,000 (negative, year 0), followed by net
revenue of NTD 300/year for 4 years.

```{r ex-compute-npv}
cash_flows <- c(-1000, 300, 300, 300, 300)

compute_npv(cash_flows, discount_rate = 0.08)
```

# Summary

```{r summary}
results <- list(
  fill_daily_na      = test_file(here("tests", "test_fill_daily_na.R"),      reporter = "silent"),
  estimate_daily_ssl = test_file(here("tests", "test_estimate_daily_ssl.R"), reporter = "silent"),
  compute_npv        = test_file(here("tests", "test_compute_npv.R"),        reporter = "silent")
)

summary_df <- map_dfr(names(results), function(fn) {
  r <- results[[fn]]
  data.frame(
    `function`  = fn,
    n_tests     = sum(r$nb),
    passed      = sum(r$passed),
    failed      = sum(r$failed),
    errors      = sum(r$error)
  )
})

knitr::kable(summary_df)
```
