---
title: "Fengping River Hydropower — Main Analysis"
subtitle: "Financial Feasibility Frontier under Hydrological Variability"
author: "[MAYA SCANLON , WILLIAM LIEN]"
date: today
format:
  pdf:
    toc: true
    toc-depth: 2
    number-sections: true
    fig-pos: "H"
    geometry: margin=2.5cm
    fontsize: 11pt
editor: source
execute:
  echo: false
  warning: false
  message: false
  cache: true
---

```{r setup}
#| cache: false

# ── Packages ──────────────────────────────────────────────────────────────────
pkgs <- c("tidyverse", "here", "patchwork", "scales", "lubridate", "zoo")
for (p in pkgs) {
  if (!requireNamespace(p, quietly = TRUE)) install.packages(p)
}
invisible(lapply(pkgs, library, character.only = TRUE))

# Suppress Windows encoding warnings from system messages
options(warn = 0)

# ── Modules ───────────────────────────────────────────────────────────────────
source(here("module", "hydro_reservoir.R"))
source(here("module", "hydro_sediment.R"))
source(here("module", "hydro_finance.R"))
source(here("module", "hydro_climate.R"))
source(here("module", "hydro_plot.R"))
source(here("module", "hydro_test.R"))

# Run all tests before any analysis — stops execution on failure
run_all_tests()
```

```{r load-data}
#| cache: false

# ── Input data ─────────────────────────────────────────────────────────────
daily_clean  <- read_csv(here("data", "lishan_daily_clean.csv"),
                         show_col_types = FALSE) |>
  mutate(date = as.Date(date))

decadal_long <- read_csv(here("data", "lishan_decadal_long.csv"),
                         show_col_types = FALSE)

sed_clean    <- read_csv(here("data", "sediment_clean.csv"),
                         show_col_types = FALSE)

rc_params    <- read_csv(here("data", "rating_curve_params.csv"),
                         show_col_types = FALSE)

weir_design  <- read_csv(here("data", "weir_design_flow.csv"),
                         show_col_types = FALSE)

# ── Global financial parameters ────────────────────────────────────────────
#
# CAPEX scenarios (four public estimates — see CAPEX_LABELS below)
#   C1 : 2.5B — 公開資訊觀測站工程揭露 (工程分項: 土木20億 + 輸配電5億)
#   C2 : 5.0B — 最初投資計畫公告
#   C3 : 6.4B — 1999 EIA 環評可行性報告 (未調整通膨)
#   C4 : 9.7B — 2025 法說會最新揭露 (含通膨與工程範疇變更)
#
# Electricity price
#   FIT : government Feed-In Tariff, regulated purchase price from Taipower
#         NTD 2.8599/kWh  (MOEA 114年度, installed capacity > 20 MW)
#   PPA : Power Purchase Agreement with corporate buyer (e.g. RE100 enterprise)
#         NTD 6.0/kWh — typical range for Taiwan green power PPA (5–10 NTD/kWh)
#         Change PPA to 8.0 or 10.0 to test higher contract rates.
#
# Financing
#   LTV      : loan-to-value ratio (80% debt, 20% equity)
#   R_EQUITY : required equity return rate
#   PROJECT_LIFE : economic lifetime from EIA design documents (35 years)

# ── CAPEX scenarios — four public estimates ─────────────────────────────────
#
#   C1  NTD 2.5B (25億)
#       Source: 公開資訊觀測站工程合約揭露 (securities exchange disclosure)
#       Decomposition: 土木工程 20億 + 輸配電/機電 5億
#       This is the most granular bottom-up figure available.
#
#   C2  NTD 5.0B (50億)
#       Source: 最初投資計畫公告 (earliest public project announcement)
#       Pre-feasibility estimate; basis unknown; often inflated for permitting.
#
#   C3  NTD 6.4B (64億)
#       Source: 1999年環境影響評估可行性報告 (1999 EIA feasibility report)
#       Reflects 1999 construction prices; not inflation-adjusted.
#
#   C4  NTD 9.7B (97億)
#       Source: 2025年法人說明會 (2025 investor conference / earnings call)
#       Most recent figure; includes inflation and revised scope.
#
# OPEX is set as a fraction of each CAPEX (opex_ntd_yr = capex * OPEX_RATE).
# The four estimates span a 4× range — CAPEX is the dominant uncertainty driver.

CAPEX_C1  <- 2.5e9    # NTD 2.5B — 公開資訊觀測站工程揭露 (25億)
CAPEX_C2  <- 5.0e9    # NTD 5.0B — 最初公告 (50億)
CAPEX_C3  <- 6.4e9    # NTD 6.4B — 1999 EIA 環評 (64億)
CAPEX_C4  <- 9.7e9    # NTD 9.7B — 2025 法說會 (97億)

# Named vector for labelling in plots and tables
CAPEX_LABELS <- c(
  "C1: 2.5B (工程揭露)"  = CAPEX_C1,
  "C2: 5.0B (原始公告)"  = CAPEX_C2,
  "C3: 6.4B (EIA 1999)"  = CAPEX_C3,
  "C4: 9.7B (法說會 2025)" = CAPEX_C4
)

# Colour palette — light → dark maps to low → high CAPEX (more cost = more risk)
CAPEX_COLS <- c(
  "C1: 2.5B (工程揭露)"  = "#1D9E75",  # teal-green
  "C2: 5.0B (原始公告)"  = "#1D4E89",  # navy blue
  "C3: 6.4B (EIA 1999)"  = "#E07B2A",  # amber
  "C4: 9.7B (法說會 2025)" = "#8B1A4A"   # deep purple-red
)

FIT          <- 2.8599    # NTD/kWh — government FIT (MOEA 114年度, > 20 MW)
PPA          <- 6.0       # NTD/kWh — corporate PPA rate; change to 8 or 10 to test

OPEX_RATE    <- 0.01      # Annual O&M as fraction of CAPEX (1%/yr; mountain hydro typical 1-2%)

LTV          <- 0.80      # 80% debt financing
R_EQUITY     <- 0.08      # equity discount rate
PROJECT_LIFE <- 35L       # years (EIA design life)
R_LOAN_SEQ   <- seq(0, 0.10, by = 0.01)  # FFF X-axis: 0%–10%
E_FLOW_MODE  <- "recommended"             # W1 = 5.0 cms; W2 = 1.0 cms

# =============================================================================
# SPEED CONTROL — adjust these two parameters to trade off speed vs precision
# =============================================================================
#
# N_SIM_BOOTSTRAP : bootstrap replicates per CV level
#   Quick test  (dev / first run)   :   20  →   60–140 simulations  (~1 min)
#   Assignment submission           :  200  →  1400 simulations      (~5 min)
#   Publication-quality             : 1000  →  7000 simulations      (~20 min)
#
# CV_GRID_USE : CV levels on the FFF Y-axis
#   Reduced (3 levels, faster)      : c(1.5, 2.5, 3.5)
#   Full    (7 levels, publication) : c(1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0)
#
# Recommended workflow:
#   1. First run:  N_SIM = 20L,  CV_GRID = c(1.5, 2.5, 3.5)  → ~1 min
#   2. Submission: N_SIM = 200L, CV_GRID = c(1.0,...,4.0)     → ~5 min
#   3. Paper:      N_SIM = 1000L, CV_GRID = c(1.0,...,4.0)    → ~20 min
# =============================================================================

N_SIM_BOOTSTRAP <- 20L                         # ← 20 / 200 / 1000
CV_GRID_USE     <- c(1.0,1.5,2.0,2.5,3.0,3.5,4.0)            # ← c(1.5,2.5,3.5) / c(1.0,1.5,2.0,2.5,3.0,3.5,4.0)
```

# Sediment and Rating Curve

## Suspended Sediment Rating Curve

The suspended sediment load (SSL, MT/day) is estimated from daily discharge
$Q$ (cms) via a power-law rating curve calibrated on 492 field observations
(1959–2023):

$$SSL = a \cdot Q^b$$

fitted by ordinary least squares in log-log space.  Only observations flagged
`ok` with detectable sediment concentration are used; below-detection-limit
records are excluded.

```{r rating-curve}
#| fig-width: 7
#| fig-height: 5
#| fig-cap: "Suspended sediment rating curve for Fengping Creek. Each point is one field sampling event (n = 492, flag == 'ok'). The exponent b = 1.51 falls within the range [1.4, 2.5] documented for Taiwan mountain streams (Wang & Kondolf 2014; Kondolf et al. 2014)."

# Retrieve pre-fitted parameters
a_rc <- rc_params$value[rc_params$parameter == "a"]
b_rc <- rc_params$value[rc_params$parameter == "b"]
r2   <- rc_params$value[rc_params$parameter == "r_squared"]
n_rc <- as.integer(rc_params$value[rc_params$parameter == "n_points"])

# Fitted line for overlay
fit_line <- data.frame(
  Discharge_CMS = 10 ^ seq(log10(2), log10(600), length.out = 300)
) |>
  mutate(SSL = a_rc * Discharge_CMS ^ b_rc)

sed_clean |>
  filter(flag == "ok", Sus_Load_MTDay > 0) |>
  ggplot(aes(x = Discharge_CMS, y = Sus_Load_MTDay)) +
  geom_point(alpha = 0.55, colour = "#1D9E75", size = 1.8) +
  geom_line(data = fit_line, aes(x = Discharge_CMS, y = SSL),
            colour = "#D85A30", linewidth = 1.0) +
  scale_x_log10(labels = comma) +
  scale_y_log10(labels = comma) +
  labs(
    title    = "Suspended Sediment Rating Curve — Fengping Creek (1959–2023)",
    subtitle = sprintf(
      "SSL = %.3f \u00d7 Q^%.3f  |  R\u00b2 = %.3f  |  n = %d",
      a_rc, b_rc, r2, n_rc),
    x       = "Discharge Q (cms, log scale)",
    y       = "Suspended sediment load SSL (MT/day, log scale)",
    caption = paste(
      "b within expected range [1.4, 2.5] for Taiwan mountain streams.",
      "\nWang & Kondolf (2014) JAWRA 50(3):735\u2013747;",
      "Kondolf et al. (2014) Earth's Future 2(5):256\u2013280."
    )
  ) +
  theme_fengping()
```

## Reservoir Sedimentation — W1 and W2

Trap efficiency $TE$ is computed annually using the Brune (1953) curve:

$$TE_t = \frac{CI_t}{CI_t + 0.0021}, \quad CI_t = \frac{S_t}{V_{\text{annual}}}$$

where $S_t$ is the remaining effective storage (m³) and $V_{\text{annual}}$
is the mean annual inflow volume.

```{r sediment-outputs}
sed_out <- build_sediment_outputs(
  sed_csv_path = here("data", "sediment_clean.csv"),
  daily_flow   = daily_clean,
  plot_fit     = FALSE
)

# ── Compute observed mean Q at each weir for trap efficiency correction ──
# W1: direct Lishan gauge observation (242 km² watershed)
mean_Q_W1 <- mean(daily_clean$Q_cms, na.rm = TRUE)

# W2: area-scaled from W1 using monthly n-exponents (EIA Table 4.1-5)
# run_reservoir_simulation() already does this scaling; here we approximate
# using the basin-area power law with n ≈ 0.85 (annual average)
mean_Q_W2 <- mean_Q_W1 * (31 / 242) ^ 0.85

# Re-run trap efficiency with correct mean flow values
annual_ssl <- sed_out$annual_ssl_mt

sed_out$trap_W1 <- estimate_trap_efficiency(
  ssl_annual_mt = annual_ssl,
  weir_id       = "W1",
  years         = PROJECT_LIFE,
  mean_Q_cms    = mean_Q_W1
)

sed_out$trap_W2 <- estimate_trap_efficiency(
  ssl_annual_mt = annual_ssl,
  weir_id       = "W2",
  years         = PROJECT_LIFE,
  mean_Q_cms    = mean_Q_W2
)
```

```{r trap-plot}
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "Simulated trap efficiency (TE) and remaining effective storage for W1 and W2 over the 35-year project lifetime. Brune (1953) curve approximation; deposit bulk density = 1300 kg/m³ (Wang et al. 2018)."

plot_trap_efficiency(sed_out$trap_W1, sed_out$trap_W2)
```

```{r sediment-table}
#| tbl-cap: "Trap efficiency and remaining effective storage at key project milestones (years 1, 10, 20, 35)."

bind_rows(
  sed_out$trap_W1 |> mutate(Weir = "W1 Lower"),
  sed_out$trap_W2 |> mutate(Weir = "W2 Upper")
) |>
  filter(year %in% c(1, 10, 20, 35)) |>
  select(
    Weir,
    Year              = year,
    `S remaining (m³)`= S_remaining_m3,
    `TE`              = TE,
    `V loss (m³/yr)`  = V_loss_m3_yr
  ) |>
  knitr::kable(
    digits      = c(0, 0, 0, 3, 0),
    format.args = list(big.mark = ","),
    align       = "lrrrrr"
  )
```

---

# Reservoir Simulation — Historical Baseline

The pondage simulation (`simulate_one_weir()`) uses a daily Euler forward
water balance with a strict dispatch priority: (1) ecological flow, (2) power
generation up to $Q_{\text{design}}$, (3) spillage.

The 24-hour forecast model (`simulate_one_weir_forward24()`) additionally
looks ahead one day to decide how much water to retain, reducing spill during
high-flow events while smoothing generation during droughts.

Both models are run on the full historical record (1958–2025) with the
**recommended ecological flow** (W1 = 5.0 cms, W2 = 1.0 cms).

```{r baseline-sim}
sim_ror  <- run_reservoir_simulation(
  daily_flow  = daily_clean,
  e_flow_mode = E_FLOW_MODE
)

sim_pond <- run_reservoir_simulation_forward24(
  daily_flow  = daily_clean,
  e_flow_mode = E_FLOW_MODE,
  scale_w2    = TRUE
)
```

## Operation Window — Interactive Date Selection

Change `START_DATE` and `END_DATE` to inspect any period of interest.

```{r operation-window}
#| fig-width: 9
#| fig-height: 6
#| fig-cap: "W1 reservoir operation during a representative typhoon-season window. Line = inflow; stacked areas = ecological flow, power diversion, and spill. Lower panels show storage trajectory and daily energy."

# ── Adjust these dates to explore different periods ──────────────────────
START_DATE <- "2010-08-01"
END_DATE   <- "2010-08-31"
# ─────────────────────────────────────────────────────────────────────────

plot_operation_window(
  sim_df     = sim_pond$W1,
  start_date = START_DATE,
  end_date   = END_DATE,
  title_text = sprintf("W1 Pondage Operation — %s to %s", START_DATE, END_DATE)
)
```

## Annual Energy — Calendar Heatmap

```{r heatmap}
#| fig-width: 10
#| fig-height: 8
#| fig-cap: "Calendar heatmap of daily energy generation for W1 (pondage mode, 1958–2025). Dark = high generation; grey = near-zero. Typhoon-season pulses visible as dark horizontal bands in July–September."

plot_energy_calendar_heatmap(sim_pond$W1, weir_label = "W1")
```

## Annual Generation Summary — Run-of-River vs Pondage

```{r annual-gen-table}
#| tbl-cap: "Annual generation statistics for W1 + W2 combined. Revenue computed at PPA rate (NTD 6.0/kWh). Run-of-river = immediate dispatch; Pondage = 24-hour forecast-informed. Historical record 1958–2025."

ann_ror <- sim_ror$combined |>
  mutate(year = year(date)) |>
  group_by(year) |>
  summarise(
    gwh_total = sum(energy_kwh_total, na.rm = TRUE) / 1e6,
    rev_ntd   = sum(energy_kwh_total, na.rm = TRUE) * PPA,
    .groups   = "drop"
  )

ann_pond <- sim_pond$combined |>
  mutate(year = year(date)) |>
  group_by(year) |>
  summarise(
    gwh_total = sum(energy_kwh_total, na.rm = TRUE) / 1e6,
    rev_ntd   = sum(energy_kwh_total, na.rm = TRUE) * PPA,
    .groups   = "drop"
  )

data.frame(
  Mode                    = c("Run-of-river", "Pondage (24-hr)"),
  `Mean GWh/yr`           = c(round(mean(ann_ror$gwh_total),              1),
                               round(mean(ann_pond$gwh_total),             1)),
  `P10 GWh/yr`            = c(round(quantile(ann_ror$gwh_total,  0.10),   1),
                               round(quantile(ann_pond$gwh_total, 0.10),   1)),
  `P90 GWh/yr`            = c(round(quantile(ann_ror$gwh_total,  0.90),   1),
                               round(quantile(ann_pond$gwh_total, 0.90),   1)),
  `Mean Revenue (NTD B/yr)`= c(round(mean(ann_ror$rev_ntd)  / 1e9,        3),
                                round(mean(ann_pond$rev_ntd) / 1e9,        3)),
  check.names = FALSE
) |>
  knitr::kable(align = "lrrrr")
```

---

# 35-Year NPV Trajectory — Historical Baseline

NPV is computed using equity discount rate $r_e = 8\%$, LTV = 80%, and
loan rate $r_{\ell} = 3\%$.  Electricity revenue uses the PPA rate
(NTD `r PPA`/kWh).  All four publicly disclosed CAPEX estimates are compared:

| Label | CAPEX | Source |
|---|---|---|
| C1 | NTD 2.5B (25億) | 公開資訊觀測站工程合約揭露：土木 20億 + 輸配電 5億 |
| C2 | NTD 5.0B (50億) | 最初投資計畫公告 (earliest public announcement) |
| C3 | NTD 6.4B (64億) | 1999年環境影響評估可行性報告 (EIA feasibility report) |
| C4 | NTD 9.7B (97億) | 2025年法人說明會 (investor conference, most recent) |

```{r npv-trajectory}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "35-year cumulative NPV trajectory (historical mean revenue, loan rate = 3%). Solid lines = pondage; dashed = run-of-river. Four CAPEX scenarios from four public sources. Revenue at PPA rate (NTD 6.0/kWh); equity discount rate 8%; LTV 80%. Horizontal dashed line = NPV breakeven."

# Helper: build cumulative NPV trajectory for one (revenue source, CAPEX) combo
make_npv_traj <- function(ann_df, capex, capex_label, mode_label) {
  rev <- mean(ann_df$rev_ntd, na.rm = TRUE)
  cf  <- build_cash_flows(
    annual_revenue_ntd = rev,
    ltv             = LTV,
    r_loan          = 0.03,
    capex_ntd       = capex,
    opex_ntd_yr     = capex * OPEX_RATE,
    project_life_yr = PROJECT_LIFE
  )
  t   <- seq_along(cf) - 1L
  dcf <- cf / (1 + R_EQUITY) ^ t
  data.frame(
    year                 = t,
    cash_flow_ntd        = cf,
    discounted_cf_ntd    = dcf,
    cumulative_npv_b_ntd = cumsum(dcf) / 1e9,
    capex_label          = capex_label,
    mode_label           = mode_label
  )
}

traj_df <- bind_rows(
  make_npv_traj(ann_ror,  CAPEX_C1, "C1: 2.5B (工程揭露)",  "Run-of-river"),
  make_npv_traj(ann_ror,  CAPEX_C2, "C2: 5.0B (原始公告)",  "Run-of-river"),
  make_npv_traj(ann_ror,  CAPEX_C3, "C3: 6.4B (EIA 1999)",  "Run-of-river"),
  make_npv_traj(ann_ror,  CAPEX_C4, "C4: 9.7B (法說會 2025)", "Run-of-river"),
  make_npv_traj(ann_pond, CAPEX_C1, "C1: 2.5B (工程揭露)",  "Pondage"),
  make_npv_traj(ann_pond, CAPEX_C2, "C2: 5.0B (原始公告)",  "Pondage"),
  make_npv_traj(ann_pond, CAPEX_C3, "C3: 6.4B (EIA 1999)",  "Pondage"),
  make_npv_traj(ann_pond, CAPEX_C4, "C4: 9.7B (法說會 2025)", "Pondage")
) |>
  mutate(
    capex_label = factor(capex_label, levels = names(CAPEX_COLS))
  )

ggplot(traj_df, aes(x = year, y = cumulative_npv_b_ntd,
                    colour = capex_label, linetype = mode_label)) +
  geom_hline(yintercept = 0, linetype = "dashed",
             colour = "grey40", linewidth = 0.4) +
  geom_line(linewidth = 0.85) +
  scale_colour_manual(values = CAPEX_COLS, name = "CAPEX scenario") +
  scale_linetype_manual(
    values = c("Run-of-river" = "dashed", "Pondage" = "solid"),
    name   = "Operation mode"
  ) +
  scale_x_continuous(breaks = seq(0, PROJECT_LIFE, by = 5)) +
  scale_y_continuous(labels = function(x) paste0(x, "B")) +
  labs(
    title    = paste0(PROJECT_LIFE, "-Year Cumulative NPV — W1 + W2 Combined"),
    subtitle = paste0(
      "PPA = NTD ", PPA, "/kWh | equity rate = ", R_EQUITY * 100,
      "% | LTV = ", LTV * 100, "% | loan rate = 3% | OPEX = ",
      OPEX_RATE * 100, "% of CAPEX/yr"
    ),
    x       = "Project year",
    y       = "Cumulative NPV (NTD billion)",
    caption = paste(
      "Historical mean annual revenue used (1958–2025).",
      "Four CAPEX estimates from: 公開資訊觀測站 (C1),",
      "原始公告 (C2), EIA 1999 (C3), 法說會 2025 (C4)."
    )
  ) +
  theme_fengping()
```

```{r npv-milestone-table}
#| tbl-cap: "Cumulative discounted NPV (NTD billion) at milestone years for four CAPEX scenarios and two operation modes. Loan rate = 3%; equity discount rate = 8%; LTV = 80%; PPA = NTD 6.0/kWh. Positive = project has recovered equity investment on a discounted basis."

traj_df |>
  filter(year %in% c(5, 10, 20, 35)) |>
  mutate(
    cell = sprintf("%.2f", cumulative_npv_b_ntd),
    col_label = paste0(mode_label, " / Yr ", year)
  ) |>
  select(capex_label, mode_label, year, cumulative_npv_b_ntd) |>
  tidyr::pivot_wider(
    names_from  = c(mode_label, year),
    names_glue  = "{mode_label} Yr{year}",
    values_from = cumulative_npv_b_ntd
  ) |>
  mutate(across(where(is.numeric), ~ sprintf("%.2f", .))) |>
  rename(CAPEX = capex_label) |>
  knitr::kable(align = paste0("l", strrep("r", 8)))
```

---

# Climate Bootstrap — Hydrological Variability Ensemble

## Bootstrap Design

Two-layer bootstrap (Section 3 of `hydro_climate.R`):

1. **Layer 1 — Whole-year block bootstrap**: draw complete calendar years
   with replacement from the observed record (1958–2025), preserving
   within-year seasonal structure and typhoon event integrity.

2. **Layer 2 — CV scaling**: rescale daily flows around the annual mean to
   a target within-year CV level:

$$Q_{\text{scaled}}(t) = \mu_{yr} + (Q_{\text{boot}}(t) - \mu_{yr}) \times \lambda, \quad \lambda = \frac{CV_{\text{target}}}{CV_{\text{boot}}}$$

This preserves $\mu_{yr}$ exactly while enabling CV values beyond the
historical range, consistent with SSP2-4.5 and SSP5-8.5 projections for
eastern Taiwan (Shiau & Huang 2014; Tung et al. 2016; IPCC AR6 Ch. 11).

```{r climate-bootstrap}
#| cache: true

# N_SIM_BOOTSTRAP and CV_GRID_USE are set in the load-data chunk.
# Increase N_SIM_BOOTSTRAP to 200 (submission) or 1000 (publication).
climate <- build_climate_ensemble(
  daily_flow  = daily_clean,
  cv_grid     = CV_GRID_USE,       # c(1.5,2.5,3.5) quick | c(1.0,...,4.0) full
  n_sim       = N_SIM_BOOTSTRAP,   # 20 quick | 200 submission | 1000 publication
  seed        = 42L,
  keep_series = TRUE                # must be TRUE for run_fff_grid()
)

message(sprintf(
  "Bootstrap ensemble: %d CV levels × %d sims = %d synthetic years",
  length(CV_GRID_USE), N_SIM_BOOTSTRAP,
  length(CV_GRID_USE) * N_SIM_BOOTSTRAP
))
```

## CV Scaling Validation

```{r cv-validation}
#| fig-width: 8
#| fig-height: 4
#| fig-cap: "Validation of Layer-2 CV scaling. Violin plots show the distribution of achieved CV across 200 bootstrap replicates for each target CV level. Diamonds mark the target. The median should lie close to each target; slight underestimation at high CV levels is expected due to the physical flow floor constraint."

plot_cv_distribution(climate$grid_df)
```

```{r mu-preservation}
#| fig-width: 8
#| fig-height: 4
#| fig-cap: "Mean-preservation check: annual mean flow (mu_yr) should be approximately constant across CV levels, confirming that Layer 2 does not alter the mean — only the variability."

plot_mu_by_cv(climate$grid_df)
```

## Historical CV Trend

```{r cv-trend}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "Historical within-year CV (1958–2025) and projected future variability scenario bands (2026–2060). Left zone: observed annual CV (grey points) with 10-year rolling mean (orange). Right zone: literature-based scenario proxies — Baseline (CV 1.5–2.5), Moderate/SSP2-4.5 (CV 2.5–3.0), High/SSP5-8.5 (CV 3.0–4.0). Vertical dashed line separates observed history from projected window. Sources: Shiau & Huang (2014); Tung et al. (2016); IPCC AR6 WGI Ch.11 (2021)."

plot_historical_cv_trend(
  annual_stats = climate$annual_stats,
  cv_grid      = CV_GRID_USE
)
```

## Bootstrap CV Distribution — Option A (target CV on X-axis)

```{r cv-bootstrap-A}
#| fig-width: 7
#| fig-height: 5
#| fig-cap: "Option A: Bootstrap CV scaling validation. X-axis = target CV level; Y-axis = achieved CV per synthetic year. Each point is one bootstrap replicate. Diamond = perfect 1:1 target. Background bands show scenario zones. Median should align with diamond."

plot_bootstrap_cv_A(climate$grid_df)
```

## Bootstrap CV Distribution — Option B (all simulations coloured by level)

```{r cv-bootstrap-B}
#| fig-width: 8
#| fig-height: 4
#| fig-cap: "Option B: Full bootstrap ensemble. Each point is one synthetic year, coloured by target CV level. Horizontal lines show median per CV level. Background bands show scenario zones."

plot_bootstrap_cv_B(climate$grid_df)
```

## Combined: Historical + Bootstrap Option A

```{r cv-combined-A}
#| fig-width: 13
#| fig-height: 5
#| fig-cap: "Combined view: historical CV trend (left) and bootstrap CV distribution by target level (right, Option A). Y-axes are aligned so CV values can be read across both panels."

plot_cv_combined(
  annual_stats = climate$annual_stats,
  grid_df      = climate$grid_df,
  option       = "A",
  cv_grid      = CV_GRID_USE,
  widths       = c(2.2, 1)
)
```

## Combined: Historical + Bootstrap Option B

```{r cv-combined-B}
#| fig-width: 13
#| fig-height: 5
#| fig-cap: "Combined view: historical CV trend (left) and full bootstrap ensemble coloured by target CV level (right, Option B)."

plot_cv_combined(
  annual_stats = climate$annual_stats,
  grid_df      = climate$grid_df,
  option       = "B",
  cv_grid      = CV_GRID_USE,
  widths       = c(2, 1.2)
)
```

---

# Financial Feasibility Frontier (FFF)

## Computation

For each of the `r nrow(climate$grid_df)` synthetic years in the bootstrap
grid, both operation modes are simulated using `run_fff_grid()`, which calls
`run_reservoir_simulation()` (run-of-river) and
`run_reservoir_simulation_forward24()` (pondage) on the full synthetic daily
flow series.  Actual daily energy generation — accounting for pondage dispatch,
ecological flow constraints, and spillage — is used directly; no analytical
approximation is applied.

NPV is computed for each loan interest rate $r_\ell \in [0\%, 10\%]$ and both
operation modes, separately for all four CAPEX estimates.

```{r fff-compute}
#| cache: true

# Expected computation time (sequential):
#   N_SIM = 20,  3 CV levels  →  60 sims   ~10-30 sec
#   N_SIM = 200, 7 CV levels  →  1400 sims ~3-5 min

run_fff <- function(capex, label) {
  run_fff_grid(
    grid_df         = climate$grid_df,
    r_loan_seq      = R_LOAN_SEQ,
    ltv             = LTV,
    r_equity        = R_EQUITY,
    e_flow_mode     = E_FLOW_MODE,
    capex_ntd       = capex,
    opex_ntd_yr     = capex * OPEX_RATE,
    project_life_yr = PROJECT_LIFE,
    fit_ntd_per_kwh = PPA,
    scale_w2        = TRUE
  ) |>
  mutate(
    mode = recode(mode,
                  "run_of_river" = "Run-of-river",
                  "pondage"      = "Pondage"),
    capex_label = label
  )
}

message("FFF — C1: 2.5B"); fff_c1 <- run_fff(CAPEX_C1, "C1: 2.5B (工程揭露)")
message("FFF — C2: 5.0B"); fff_c2 <- run_fff(CAPEX_C2, "C2: 5.0B (原始公告)")
message("FFF — C3: 6.4B"); fff_c3 <- run_fff(CAPEX_C3, "C3: 6.4B (EIA 1999)")
message("FFF — C4: 9.7B"); fff_c4 <- run_fff(CAPEX_C4, "C4: 9.7B (法說會 2025)")

fff_c1_sum <- summarise_fff_grid(fff_c1)
fff_c2_sum <- summarise_fff_grid(fff_c2)
fff_c3_sum <- summarise_fff_grid(fff_c3)
fff_c4_sum <- summarise_fff_grid(fff_c4)
```

```{r fff-overview-table}
#| tbl-cap: "Median NPV (NTD B) and P(NPV > 0) for pondage mode at loan rate = 3%, across four CAPEX estimates and all CV levels. Format: median NPV (viability %)."

make_fff_row <- function(df, capex_label) {
  df |>
    filter(mode == "Pondage", abs(r_loan_pct - 3) < 0.01) |>
    mutate(
      cell        = sprintf("%.1f B / %.0f%%", npv_mean, prob_viable * 100),
      CAPEX       = capex_label,
      `CV level`  = cv_level
    ) |>
    select(CAPEX, `CV level`, cell)
}

bind_rows(
  make_fff_row(fff_c1_sum, "C1: 2.5B (工程揭露)"),
  make_fff_row(fff_c2_sum, "C2: 5.0B (原始公告)"),
  make_fff_row(fff_c3_sum, "C3: 6.4B (EIA 1999)"),
  make_fff_row(fff_c4_sum, "C4: 9.7B (法說會 2025)")
) |>
  tidyr::pivot_wider(names_from = `CV level`, values_from = cell,
                     names_prefix = "CV = ") |>
  knitr::kable(align = paste0("l", strrep("r", length(CV_GRID_USE))))
```

## Cross-CAPEX Overview Table

See the `fff-overview-table` above for a unified summary across all four CAPEX
estimates at $r_\ell = 3\%$.  Individual per-CAPEX tables (at all loan rates)
follow each FFF heatmap below.

## C1 — CAPEX NTD 2.5B (公開資訊觀測站工程揭露)

```{r fff-c1-table}
#| tbl-cap: "C1 (CAPEX = NTD 2.5B, pondage mode): E[NPV] (NTD B) and P(NPV > 0) at each CV level and loan rate. Format: E[NPV] B / P(viable %)."

fff_c1_sum |>
  filter(mode == "Pondage") |>
  mutate(cell    = sprintf("%.1f / %.0f%%", npv_mean, prob_viable * 100),
         r_label = paste0(sprintf("%.0f", r_loan_pct), "%")) |>
  select(cv_level, r_label, cell) |>
  tidyr::pivot_wider(names_from = r_label, values_from = cell) |>
  arrange(cv_level) |>
  rename(`CV level` = cv_level) |>
  knitr::kable(align = paste0("r", strrep("r", length(R_LOAN_SEQ))))
```

```{r fff-c1-enpv}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "C1 E[NPV] — CAPEX = NTD 2.5B: Expected NPV (NTD billion) across bootstrap replicates. Cell labels show mean profit/loss in NTD B. Deep green = large expected profit; deep purple-red = large expected loss. Black contour = E[NPV] = 0 (break-even)."

plot_fff_npv_mean_comparison(
  fff_c1_sum,
  title_text = "E[NPV] — C1: CAPEX = NTD 2.5B (公開資訊觀測站工程揭露)"
)
```

```{r fff-c1-prob}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "C1 P(NPV > 0) — CAPEX = NTD 2.5B: Probability of positive NPV across bootstrap replicates. Deep green = high confidence profitable; deep purple-red = high confidence loss. Black contour = 50% (most-likely breakeven boundary)."

plot_fff_mode_comparison(
  fff_c1_sum,
  title_text = "P(NPV > 0) — C1: CAPEX = NTD 2.5B (公開資訊觀測站工程揭露)"
)
```

## C2 — CAPEX NTD 5.0B (最初投資計畫公告)

```{r fff-c2-table}
#| tbl-cap: "C2 (CAPEX = NTD 5.0B, pondage mode): E[NPV] (NTD B) and P(NPV > 0). Format: E[NPV] B / P(viable %)."

fff_c2_sum |>
  filter(mode == "Pondage") |>
  mutate(cell    = sprintf("%.1f / %.0f%%", npv_mean, prob_viable * 100),
         r_label = paste0(sprintf("%.0f", r_loan_pct), "%")) |>
  select(cv_level, r_label, cell) |>
  tidyr::pivot_wider(names_from = r_label, values_from = cell) |>
  arrange(cv_level) |>
  rename(`CV level` = cv_level) |>
  knitr::kable(align = paste0("r", strrep("r", length(R_LOAN_SEQ))))
```

```{r fff-c2-enpv}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "C2 E[NPV] — CAPEX = NTD 5.0B (最初投資計畫公告). Expected profit/loss in NTD B per cell. Black contour = break-even."

plot_fff_npv_mean_comparison(
  fff_c2_sum,
  title_text = "E[NPV] — C2: CAPEX = NTD 5.0B (最初投資計畫公告)"
)
```

```{r fff-c2-prob}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "C2 P(NPV > 0) — CAPEX = NTD 5.0B. Probability of financial viability. Black contour = 50% boundary."

plot_fff_mode_comparison(
  fff_c2_sum,
  title_text = "P(NPV > 0) — C2: CAPEX = NTD 5.0B (最初投資計畫公告)"
)
```

## C3 — CAPEX NTD 6.4B (1999 EIA 環評)

```{r fff-c3-table}
#| tbl-cap: "C3 (CAPEX = NTD 6.4B, pondage mode): E[NPV] (NTD B) and P(NPV > 0). Format: E[NPV] B / P(viable %)."

fff_c3_sum |>
  filter(mode == "Pondage") |>
  mutate(cell    = sprintf("%.1f / %.0f%%", npv_mean, prob_viable * 100),
         r_label = paste0(sprintf("%.0f", r_loan_pct), "%")) |>
  select(cv_level, r_label, cell) |>
  tidyr::pivot_wider(names_from = r_label, values_from = cell) |>
  arrange(cv_level) |>
  rename(`CV level` = cv_level) |>
  knitr::kable(align = paste0("r", strrep("r", length(R_LOAN_SEQ))))
```

```{r fff-c3-enpv}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "C3 E[NPV] — CAPEX = NTD 6.4B (1999 EIA 環評可行性報告). Expected profit/loss in NTD B. Note: 1999 figure not adjusted for inflation."

plot_fff_npv_mean_comparison(
  fff_c3_sum,
  title_text = "E[NPV] — C3: CAPEX = NTD 6.4B (1999 EIA 環評可行性報告)"
)
```

```{r fff-c3-prob}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "C3 P(NPV > 0) — CAPEX = NTD 6.4B. Probability of financial viability across bootstrap climate ensemble."

plot_fff_mode_comparison(
  fff_c3_sum,
  title_text = "P(NPV > 0) — C3: CAPEX = NTD 6.4B (1999 EIA 環評可行性報告)"
)
```

## C4 — CAPEX NTD 9.7B (2025 法說會)

```{r fff-c4-table}
#| tbl-cap: "C4 (CAPEX = NTD 9.7B, pondage mode): E[NPV] (NTD B) and P(NPV > 0). Format: E[NPV] B / P(viable %)."

fff_c4_sum |>
  filter(mode == "Pondage") |>
  mutate(cell    = sprintf("%.1f / %.0f%%", npv_mean, prob_viable * 100),
         r_label = paste0(sprintf("%.0f", r_loan_pct), "%")) |>
  select(cv_level, r_label, cell) |>
  tidyr::pivot_wider(names_from = r_label, values_from = cell) |>
  arrange(cv_level) |>
  rename(`CV level` = cv_level) |>
  knitr::kable(align = paste0("r", strrep("r", length(R_LOAN_SEQ))))
```

```{r fff-c4-enpv}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "C4 E[NPV] — CAPEX = NTD 9.7B (2025年法說會最新揭露). At this cost level most cells show negative E[NPV]; viable corridor confined to very low loan rates under historical CV."

plot_fff_npv_mean_comparison(
  fff_c4_sum,
  title_text = "E[NPV] — C4: CAPEX = NTD 9.7B (2025 法說會最新揭露)"
)
```

```{r fff-c4-prob}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "C4 P(NPV > 0) — CAPEX = NTD 9.7B. Probability of positive NPV. Viable region is narrow even under pondage mode."

plot_fff_mode_comparison(
  fff_c4_sum,
  title_text = "P(NPV > 0) — C4: CAPEX = NTD 9.7B (2025 法說會最新揭露)"
)
```

## Summary — E[NPV] across all CAPEX estimates (Pondage mode)

```{r fff-enpv-summary}
#| fig-width: 12
#| fig-height: 10
#| fig-cap: "Summary: E[NPV] (NTD billion) for pondage mode across all four CAPEX estimates. Each panel = one cost scenario. Cell labels show expected profit (+) or loss (−) in NTD B. Black contour = break-even. Reading across panels shows how CAPEX is the dominant uncertainty: C1 (25億) is widely profitable, C4 (97億) is largely unprofitable under the same revenue assumptions."

plot_fff_enpv_all_capex(
  list(
    "C1: 2.5B (工程揭露)"    = fff_c1_sum,
    "C2: 5.0B (原始公告)"    = fff_c2_sum,
    "C3: 6.4B (EIA 1999)"    = fff_c3_sum,
    "C4: 9.7B (法說會 2025)" = fff_c4_sum
  ),
  title_text = "E[NPV] Summary — Pondage Mode, Four CAPEX Estimates"
)
```

## Pondage Advantage — Difference in P(NPV > 0)

```{r fff-diff}
#| fig-width: 9
#| fig-height: 4
#| fig-cap: "Difference in P(NPV > 0) between pondage and run-of-river operation. Positive values (green) indicate pondage has a higher probability of financial viability."

# Note: after recode() in fff-compute, mode values are "Pondage" and
# "Run-of-river" (title-case with hyphen).  pivot_wider creates columns
# with those exact names, so backtick-quote them in mutate().
diff_df <- fff_c1_sum |>
  select(cv_level, r_loan_pct, mode, prob_viable) |>
  tidyr::pivot_wider(names_from = mode, values_from = prob_viable) |>
  mutate(delta_prob = Pondage - `Run-of-river`)

ggplot(diff_df, aes(x = r_loan_pct, y = cv_level, fill = delta_prob)) +
  geom_tile(colour = "white", linewidth = 0.25) +
  geom_contour(aes(z = delta_prob), breaks = 0,
               colour = "black", linewidth = 0.8, linetype = "dashed") +
  scale_fill_gradient2(
    low      = "#8B1A4A",
    mid      = "#F5F0F4",
    high     = "#1D9E75",
    midpoint = 0,
    labels   = scales::percent,
    name     = expression(Delta * "P(NPV>0)")
  ) +
  scale_x_continuous(labels = function(x) paste0(x, "%"),
                     breaks = R_LOAN_SEQ * 100) +
  scale_y_continuous(breaks = CV_GRID_USE) +
  labs(
    title    = "Pondage Advantage over Run-of-River",
    subtitle = expression(
      "Difference in P(NPV>0): " * Delta == P[Pondage] - P["Run-of-river"]),
    x        = "Loan interest rate (%)",
    y        = "Within-year flow CV",
    caption  = paste0(
      "Shown for C1 (CAPEX = NTD 2.5B); LTV = ", LTV * 100, "%; equity rate = ",
      R_EQUITY * 100, "%; project life = ", PROJECT_LIFE, " yr.",
      "\nPositive delta (green): pondage achieves higher P(NPV>0) than run-of-river.",
      "\nPattern is consistent across all four CAPEX estimates (C1–C4)."
    )
  ) +
  theme_fengping() +
  theme(panel.grid = element_blank(), legend.position = "right")
```

---

# Summary and Policy Implications

```{r summary-table}
#| tbl-cap: "Summary of key results by CAPEX scenario. Viability defined as P(NPV > 0) >= 0.50 (Pondage mode, r_loan = 3%). Revenue at PPA rate (NTD 6.0/kWh)."

extract_viability <- function(summ_df, capex_label) {
  summ_df |>
    filter(mode == "Pondage", abs(r_loan_pct - 3) < 0.01) |>
    select(cv_level, prob_viable, npv_mean, gwh_P50) |>
    mutate(capex = capex_label)
}

bind_rows(
  extract_viability(fff_c1_sum, "C1: 2.5B (Stock Exchange Disclosure of Civil and Engineering Cost)"),
  extract_viability(fff_c2_sum, "C2: 5.0B (Original 1999)"),
  extract_viability(fff_c3_sum, "C3: 6.4B (Updated EIA 2020)"),
  extract_viability(fff_c4_sum, "C4: 9.7B (Investor Relation Meeting 2025)")
) |>
  mutate(
    viable_flag = if_else(prob_viable >= 0.5, "Yes", "No"),
    CV_label    = paste0("CV = ", cv_level)
  ) |>
  select(
    CAPEX               = capex,
    `CV level`          = CV_label,
    `P(NPV>0)`          = prob_viable,
    `E[NPV] (NTD B)`    = npv_mean,
    `Median GWh/yr`     = gwh_P50,
    `Viable?`           = viable_flag
  ) |>
  knitr::kable(digits = c(0, 0, 2, 2, 1, 0))
```

The Financial Feasibility Frontier reveals that:

1. **Pondage consistently outperforms run-of-river** across all CV levels,
   loan rates, and CAPEX estimates, confirming that even the small pondage
   capacity of W1 and W2 provides measurable financial value through improved
   dispatch flexibility.

2. **CAPEX is the dominant uncertainty driver** — spanning a 4× range (2.5B to
   9.7B) across public sources.  Under C1 (NTD 2.5B, engineering disclosure),
   both modes are widely viable at historical CV.  Under C4 (NTD 9.7B, 2025
   法說會), viability requires loan rates ≤ 2–3% under historical CV, and is
   essentially infeasible at elevated CV — confirming that cost verification is
   the critical prerequisite before project financing.

3. **Higher hydrological variability (CV > 2.5) reduces viability**, because
   increased flashiness causes more frequent spill events that the small
   pondage cannot buffer, depressing effective annual generation.  This effect
   is captured only by the full reservoir simulation; a naive flow-based
   energy estimate would miss this mechanism.

4. **Under SSP5-8.5 projections (CV ≈ 3.0–4.0)**, even under C1 (lowest
   CAPEX), pondage viability requires loan rates below 5–6%, suggesting that
   climate change imposes a meaningful financing-cost premium on flash-flood
   dominated catchments in Taiwan.

```{r teardown}
#| cache: false
# Analysis complete.
message("fp_hydro_main.qmd render complete.")
```
