---
title: "Fengping River Hydropower — Main Analysis"
subtitle: "Financial Feasibility Frontier under Hydrological Variability"
author: "[your name]"
date: today
format:
  pdf:
    toc: true
    toc-depth: 2
    number-sections: true
    fig-pos: "H"
    geometry: margin=2.5cm
    fontsize: 11pt
editor: source
execute:
  echo: false
  warning: false
  message: false
  cache: true
---

```{r setup}
#| cache: false

# ── Packages ──────────────────────────────────────────────────────────────────
pkgs <- c("tidyverse", "here", "patchwork", "scales", "lubridate", "zoo")
for (p in pkgs) {
  if (!requireNamespace(p, quietly = TRUE)) install.packages(p)
}
invisible(lapply(pkgs, library, character.only = TRUE))

# Suppress Windows encoding warnings from system messages
options(warn = 0)

# ── Modules ───────────────────────────────────────────────────────────────────
source(here("module", "hydro_reservoir.R"))
source(here("module", "hydro_sediment.R"))
source(here("module", "hydro_finance.R"))
source(here("module", "hydro_climate.R"))
source(here("module", "hydro_plot.R"))
source(here("module", "hydro_test.R"))

# Run all tests before any analysis — stops execution on failure
run_all_tests()
```

```{r load-data}
#| cache: false

# ── Input data ─────────────────────────────────────────────────────────────
daily_clean  <- read_csv(here("data", "lishan_daily_clean.csv"),
                         show_col_types = FALSE) |>
  mutate(date = as.Date(date))

decadal_long <- read_csv(here("data", "lishan_decadal_long.csv"),
                         show_col_types = FALSE)

sed_clean    <- read_csv(here("data", "sediment_clean.csv"),
                         show_col_types = FALSE)

rc_params    <- read_csv(here("data", "rating_curve_params.csv"),
                         show_col_types = FALSE)

weir_design  <- read_csv(here("data", "weir_design_flow.csv"),
                         show_col_types = FALSE)

# ── Global financial parameters ────────────────────────────────────────────
#
# CAPEX scenarios
#   CAPEX_OG   : earliest public estimate at project announcement (~NTD 5.0B)
#   CAPEX_EIA  : 1999 EIA feasibility report estimate (NTD 6.4B)
#   CAPEX_2025 : 2025 investor conference updated estimate (NTD 9.7B)
#                (reflects inflation, material cost increases since 1999)
#
# Electricity price
#   FIT : government Feed-In Tariff, regulated purchase price from Taipower
#         NTD 2.8599/kWh  (MOEA 114年度, installed capacity > 20 MW)
#   PPA : Power Purchase Agreement with corporate buyer (e.g. RE100 enterprise)
#         NTD 6.0/kWh — typical range for Taiwan green power PPA (5–10 NTD/kWh)
#         Change PPA to 8.0 or 10.0 to test higher contract rates.
#
# Financing
#   LTV      : loan-to-value ratio (80% debt, 20% equity)
#   R_EQUITY : required equity return rate
#   PROJECT_LIFE : economic lifetime from EIA design documents (35 years)

CAPEX_OG     <- 5.0e9     # NTD — earliest public project announcement
CAPEX_EIA    <- 6.4e9     # NTD — 1999 EIA feasibility report
CAPEX_2025   <- 9.7e9     # NTD — 2025 investor conference (updated)

FIT          <- 2.8599    # NTD/kWh — government FIT (MOEA 114年度, > 20 MW)
PPA          <- 6.0       # NTD/kWh — corporate PPA rate; change to 8 or 10 to test

OPEX_RATE    <- 0.01      # O&M as fraction of CAPEX (1% rule of thumb)

LTV          <- 0.80      # 80% debt financing
R_EQUITY     <- 0.08      # equity discount rate
PROJECT_LIFE <- 35L       # years (EIA design life)
R_LOAN_SEQ   <- seq(0, 0.10, by = 0.01)  # FFF X-axis: 0%–10%
E_FLOW_MODE  <- "recommended"             # W1 = 5.0 cms; W2 = 1.0 cms

# =============================================================================
# SPEED CONTROL — adjust these two parameters to trade off speed vs precision
# =============================================================================
#
# N_SIM_BOOTSTRAP : bootstrap replicates per CV level
#   Quick test  (dev / first run)   :   20  →   60–140 simulations  (~1 min)
#   Assignment submission           :  200  →  1400 simulations      (~5 min)
#   Publication-quality             : 1000  →  7000 simulations      (~20 min)
#
# CV_GRID_USE : CV levels on the FFF Y-axis
#   Reduced (3 levels, faster)      : c(1.5, 2.5, 3.5)
#   Full    (7 levels, publication) : c(1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0)
#
# Recommended workflow:
#   1. First run:  N_SIM = 20L,  CV_GRID = c(1.5, 2.5, 3.5)  → ~1 min
#   2. Submission: N_SIM = 200L, CV_GRID = c(1.0,...,4.0)     → ~5 min
#   3. Paper:      N_SIM = 1000L, CV_GRID = c(1.0,...,4.0)    → ~20 min
# =============================================================================

N_SIM_BOOTSTRAP <- 20L                         # ← 20 / 200 / 1000
CV_GRID_USE     <- c(1.5, 2.5, 3.5)            # ← c(1.5,2.5,3.5) / c(1.0,1.5,2.0,2.5,3.0,3.5,4.0)
```

# Sediment and Rating Curve

## Suspended Sediment Rating Curve

The suspended sediment load (SSL, MT/day) is estimated from daily discharge
$Q$ (cms) via a power-law rating curve calibrated on 492 field observations
(1959–2023):

$$SSL = a \cdot Q^b$$

fitted by ordinary least squares in log-log space.  Only observations flagged
`ok` with detectable sediment concentration are used; below-detection-limit
records are excluded.

```{r rating-curve}
#| fig-width: 7
#| fig-height: 5
#| fig-cap: "Suspended sediment rating curve for Fengping Creek. Each point is one field sampling event (n = 492, flag == 'ok'). The exponent b = 1.51 falls within the range [1.4, 2.5] documented for Taiwan mountain streams (Wang & Kondolf 2014; Kondolf et al. 2014)."

# Retrieve pre-fitted parameters
a_rc <- rc_params$value[rc_params$parameter == "a"]
b_rc <- rc_params$value[rc_params$parameter == "b"]
r2   <- rc_params$value[rc_params$parameter == "r_squared"]
n_rc <- as.integer(rc_params$value[rc_params$parameter == "n_points"])

# Fitted line for overlay
fit_line <- data.frame(
  Discharge_CMS = 10 ^ seq(log10(2), log10(600), length.out = 300)
) |>
  mutate(SSL = a_rc * Discharge_CMS ^ b_rc)

sed_clean |>
  filter(flag == "ok", Sus_Load_MTDay > 0) |>
  ggplot(aes(x = Discharge_CMS, y = Sus_Load_MTDay)) +
  geom_point(alpha = 0.55, colour = "#1D9E75", size = 1.8) +
  geom_line(data = fit_line, aes(x = Discharge_CMS, y = SSL),
            colour = "#D85A30", linewidth = 1.0) +
  scale_x_log10(labels = comma) +
  scale_y_log10(labels = comma) +
  labs(
    title    = "Suspended Sediment Rating Curve — Fengping Creek (1959–2023)",
    subtitle = sprintf(
      "SSL = %.3f \u00d7 Q^%.3f  |  R\u00b2 = %.3f  |  n = %d",
      a_rc, b_rc, r2, n_rc),
    x       = "Discharge Q (cms, log scale)",
    y       = "Suspended sediment load SSL (MT/day, log scale)",
    caption = paste(
      "b within expected range [1.4, 2.5] for Taiwan mountain streams.",
      "\nWang & Kondolf (2014) JAWRA 50(3):735\u2013747;",
      "Kondolf et al. (2014) Earth's Future 2(5):256\u2013280."
    )
  ) +
  theme_fengping()
```

## Reservoir Sedimentation — W1 and W2

Trap efficiency $TE$ is computed annually using the Brune (1953) curve:

$$TE_t = \frac{CI_t}{CI_t + 0.0021}, \quad CI_t = \frac{S_t}{V_{\text{annual}}}$$

where $S_t$ is the remaining effective storage (m³) and $V_{\text{annual}}$
is the mean annual inflow volume.

```{r sediment-outputs}
sed_out <- build_sediment_outputs(
  sed_csv_path = here("data", "sediment_clean.csv"),
  daily_flow   = daily_clean,
  plot_fit     = FALSE
)
```

```{r trap-plot}
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "Simulated trap efficiency (TE) and remaining effective storage for W1 and W2 over the 35-year project lifetime. Brune (1953) curve approximation; deposit bulk density = 1300 kg/m³ (Wang et al. 2018)."

plot_trap_efficiency(sed_out$trap_W1, sed_out$trap_W2)
```

```{r sediment-table}
#| tbl-cap: "Trap efficiency and remaining effective storage at key project milestones (years 1, 10, 20, 35)."

bind_rows(
  sed_out$trap_W1 |> mutate(Weir = "W1 Lower"),
  sed_out$trap_W2 |> mutate(Weir = "W2 Upper")
) |>
  filter(year %in% c(1, 10, 20, 35)) |>
  select(
    Weir,
    Year              = year,
    `S remaining (m³)`= S_remaining_m3,
    `TE`              = TE,
    `V loss (m³/yr)`  = V_loss_m3_yr
  ) |>
  knitr::kable(
    digits      = c(0, 0, 0, 3, 0),
    format.args = list(big.mark = ","),
    align       = "lrrrrr"
  )
```

---

# Reservoir Simulation — Historical Baseline

The pondage simulation (`simulate_one_weir()`) uses a daily Euler forward
water balance with a strict dispatch priority: (1) ecological flow, (2) power
generation up to $Q_{\text{design}}$, (3) spillage.

The 24-hour forecast model (`simulate_one_weir_forward24()`) additionally
looks ahead one day to decide how much water to retain, reducing spill during
high-flow events while smoothing generation during droughts.

Both models are run on the full historical record (1958–2025) with the
**recommended ecological flow** (W1 = 5.0 cms, W2 = 1.0 cms).

```{r baseline-sim}
sim_ror  <- run_reservoir_simulation(
  daily_flow  = daily_clean,
  e_flow_mode = E_FLOW_MODE
)

sim_pond <- run_reservoir_simulation_forward24(
  daily_flow  = daily_clean,
  e_flow_mode = E_FLOW_MODE,
  scale_w2    = TRUE
)
```

## Operation Window — Interactive Date Selection

Change `START_DATE` and `END_DATE` to inspect any period of interest.

```{r operation-window}
#| fig-width: 9
#| fig-height: 6
#| fig-cap: "W1 reservoir operation during a representative typhoon-season window. Line = inflow; stacked areas = ecological flow, power diversion, and spill. Lower panels show storage trajectory and daily energy."

# ── Adjust these dates to explore different periods ──────────────────────
START_DATE <- "2010-08-01"
END_DATE   <- "2010-08-31"
# ─────────────────────────────────────────────────────────────────────────

plot_operation_window(
  sim_df     = sim_pond$W1,
  start_date = START_DATE,
  end_date   = END_DATE,
  title_text = sprintf("W1 Pondage Operation — %s to %s", START_DATE, END_DATE)
)
```

## Annual Energy — Calendar Heatmap

```{r heatmap}
#| fig-width: 10
#| fig-height: 8
#| fig-cap: "Calendar heatmap of daily energy generation for W1 (pondage mode, 1958–2025). Dark = high generation; grey = near-zero. Typhoon-season pulses visible as dark horizontal bands in July–September."

plot_energy_calendar_heatmap(sim_pond$W1, weir_label = "W1")
```

## Annual Generation Summary — Run-of-River vs Pondage

```{r annual-gen-table}
#| tbl-cap: "Annual generation statistics for W1 + W2 combined. Revenue computed at PPA rate (NTD 6.0/kWh). Run-of-river = immediate dispatch; Pondage = 24-hour forecast-informed. Historical record 1958–2025."

ann_ror <- sim_ror$combined |>
  mutate(year = year(date)) |>
  group_by(year) |>
  summarise(
    gwh_total = sum(energy_kwh_total, na.rm = TRUE) / 1e6,
    rev_ntd   = sum(energy_kwh_total, na.rm = TRUE) * PPA,
    .groups   = "drop"
  )

ann_pond <- sim_pond$combined |>
  mutate(year = year(date)) |>
  group_by(year) |>
  summarise(
    gwh_total = sum(energy_kwh_total, na.rm = TRUE) / 1e6,
    rev_ntd   = sum(energy_kwh_total, na.rm = TRUE) * PPA,
    .groups   = "drop"
  )

data.frame(
  Mode                    = c("Run-of-river", "Pondage (24-hr)"),
  `Mean GWh/yr`           = c(round(mean(ann_ror$gwh_total),              1),
                               round(mean(ann_pond$gwh_total),             1)),
  `P10 GWh/yr`            = c(round(quantile(ann_ror$gwh_total,  0.10),   1),
                               round(quantile(ann_pond$gwh_total, 0.10),   1)),
  `P90 GWh/yr`            = c(round(quantile(ann_ror$gwh_total,  0.90),   1),
                               round(quantile(ann_pond$gwh_total, 0.90),   1)),
  `Mean Revenue (NTD B/yr)`= c(round(mean(ann_ror$rev_ntd)  / 1e9,        3),
                                round(mean(ann_pond$rev_ntd) / 1e9,        3)),
  check.names = FALSE
) |>
  knitr::kable(align = "lrrrr")
```

---

# 35-Year NPV Trajectory — Historical Baseline

NPV is computed using equity discount rate $r_e = 8\%$, LTV = 80%, and
loan rate $r_{\ell} = 3\%$.  Electricity revenue uses the PPA rate
(NTD `r PPA`/kWh).  Three CAPEX scenarios are compared:

- **CAPEX\textsubscript{OG}** = NTD 5.0 billion (earliest public announcement)
- **CAPEX\textsubscript{EIA}** = NTD 6.4 billion (1999 EIA feasibility report)
- **CAPEX\textsubscript{2025}** = NTD 9.7 billion (2025 investor conference)

```{r npv-trajectory}
#| fig-width: 9
#| fig-height: 5
#| fig-cap: "35-year cumulative NPV trajectory for both operation modes and three CAPEX scenarios. Revenue at PPA rate (NTD 6.0/kWh). Dashed horizontal line = NPV breakeven."

make_npv_traj <- function(ann_df, capex, label) {
  rev <- mean(ann_df$rev_ntd, na.rm = TRUE)
  # Use build_cash_flows() with PROJECT_LIFE (35yr) directly.
  # build_cash_flows_20yr() is hardcoded to 20 years; use the general version.
  cf  <- build_cash_flows(
    annual_revenue_ntd = rev,
    ltv             = LTV,
    r_loan          = 0.03,
    capex_ntd       = capex,
    opex_ntd_yr     = capex * OPEX_RATE,
    project_life_yr = PROJECT_LIFE        # 35 years
  )
  # Build year-by-year cumulative discounted NPV manually
  t    <- seq_along(cf) - 1L
  dcf  <- cf / (1 + R_EQUITY) ^ t
  data.frame(
    year                 = t,
    cash_flow_ntd        = cf,
    discounted_cf_ntd    = dcf,
    cumulative_npv_b_ntd = cumsum(dcf) / 1e9,
    label                = label
  )
}

traj_df <- bind_rows(
  make_npv_traj(ann_ror,  CAPEX_OG,   "Run-of-river / CAPEX OG (5.0B)"),
  make_npv_traj(ann_ror,  CAPEX_EIA,  "Run-of-river / CAPEX EIA (6.4B)"),
  make_npv_traj(ann_ror,  CAPEX_2025, "Run-of-river / CAPEX 2025 (9.7B)"),
  make_npv_traj(ann_pond, CAPEX_OG,   "Pondage / CAPEX OG (5.0B)"),
  make_npv_traj(ann_pond, CAPEX_EIA,  "Pondage / CAPEX EIA (6.4B)"),
  make_npv_traj(ann_pond, CAPEX_2025, "Pondage / CAPEX 2025 (9.7B)")
) |>
  mutate(
    mode_label  = if_else(grepl("Pondage", label), "Pondage", "Run-of-river"),
    capex_label = case_when(
      grepl("OG",   label) ~ "CAPEX OG (5.0B)",
      grepl("EIA",  label) ~ "CAPEX EIA (6.4B)",
      TRUE                 ~ "CAPEX 2025 (9.7B)"
    )
  )

ggplot(traj_df, aes(x = year, y = cumulative_npv_b_ntd,
                    colour = capex_label, linetype = mode_label)) +
  geom_hline(yintercept = 0, linetype = "dashed",
             colour = "grey40", linewidth = 0.4) +
  geom_line(linewidth = 0.9) +
  scale_colour_manual(
    values = c("CAPEX OG (5.0B)"   = "#1D9E75",
               "CAPEX EIA (6.4B)"  = "#1D4E89",
               "CAPEX 2025 (9.7B)" = "#D85A30"),
    name = "CAPEX scenario"
  ) +
  scale_linetype_manual(
    values = c("Run-of-river" = "dashed", "Pondage" = "solid"),
    name   = "Operation mode"
  ) +
  scale_x_continuous(breaks = seq(0, PROJECT_LIFE, by = 5)) +
  scale_y_continuous(labels = function(x) paste0(x, "B")) +
  labs(
    title    = paste0(PROJECT_LIFE, "-Year Cumulative NPV Trajectory (W1 + W2 Combined)"),
    subtitle = paste0(
      "PPA = NTD ", PPA, "/kWh; equity rate = ", R_EQUITY * 100,
      "%; LTV = ", LTV * 100, "%; loan rate = 3%; OPEX = 1% CAPEX."
    ),
    x = "Project year",
    y = "Cumulative NPV (NTD billion)"
  ) +
  theme_fengping()
```

---

# Climate Bootstrap — Hydrological Variability Ensemble

## Bootstrap Design

Two-layer bootstrap (Section 3 of `hydro_climate.R`):

1. **Layer 1 — Whole-year block bootstrap**: draw complete calendar years
   with replacement from the observed record (1958–2025), preserving
   within-year seasonal structure and typhoon event integrity.

2. **Layer 2 — CV scaling**: rescale daily flows around the annual mean to
   a target within-year CV level:

$$Q_{\text{scaled}}(t) = \mu_{yr} + (Q_{\text{boot}}(t) - \mu_{yr}) \times \lambda, \quad \lambda = \frac{CV_{\text{target}}}{CV_{\text{boot}}}$$

This preserves $\mu_{yr}$ exactly while enabling CV values beyond the
historical range, consistent with SSP2-4.5 and SSP5-8.5 projections for
eastern Taiwan (Shiau & Huang 2014; Tung et al. 2016; IPCC AR6 Ch. 11).

```{r climate-bootstrap}
#| cache: true

# N_SIM_BOOTSTRAP and CV_GRID_USE are set in the load-data chunk.
# Increase N_SIM_BOOTSTRAP to 200 (submission) or 1000 (publication).
climate <- build_climate_ensemble(
  daily_flow  = daily_clean,
  cv_grid     = CV_GRID_USE,       # c(1.5,2.5,3.5) quick | c(1.0,...,4.0) full
  n_sim       = N_SIM_BOOTSTRAP,   # 20 quick | 200 submission | 1000 publication
  seed        = 42L,
  keep_series = TRUE                # must be TRUE for run_fff_grid()
)

message(sprintf(
  "Bootstrap ensemble: %d CV levels × %d sims = %d synthetic years",
  length(CV_GRID_USE), N_SIM_BOOTSTRAP,
  length(CV_GRID_USE) * N_SIM_BOOTSTRAP
))
```

## CV Scaling Validation

```{r cv-validation}
#| fig-width: 8
#| fig-height: 4
#| fig-cap: "Validation of Layer-2 CV scaling. Violin plots show the distribution of achieved CV across 200 bootstrap replicates for each target CV level. Diamonds mark the target. The median should lie close to each target; slight underestimation at high CV levels is expected due to the physical flow floor constraint."

plot_cv_distribution(climate$grid_df)
```

```{r mu-preservation}
#| fig-width: 8
#| fig-height: 4
#| fig-cap: "Mean-preservation check: annual mean flow (mu_yr) should be approximately constant across CV levels, confirming that Layer 2 does not alter the mean — only the variability."

plot_mu_by_cv(climate$grid_df)
```

## Historical CV Trend

```{r cv-trend}
#| fig-width: 9
#| fig-height: 5
#| fig-cap: "Historical within-year CV of daily flow at Lishan Station (1958–2025) with climate-change projection bands. Grey points = annual CV; orange line = 10-year rolling mean; dashed lines = FFF target CV levels. Coloured bands correspond to CV ranges associated with historical observations (grey), SSP2-4.5 (green), and SSP5-8.5 (red) projections for 2050 (Shiau & Huang 2014; Tung et al. 2016; IPCC AR6 Ch.11 2021)."

plot_historical_cv_trend(
  annual_stats = climate$annual_stats,
  cv_grid      = CV_GRID_USE      # matches the FFF Y-axis levels in use
)
```

---

# Financial Feasibility Frontier (FFF)

## Computation

For each of the `r nrow(climate$grid_df)` synthetic years in the bootstrap
grid, both operation modes are simulated using `run_fff_grid()`, which calls
`run_reservoir_simulation()` (run-of-river) and
`run_reservoir_simulation_forward24()` (pondage) on the full synthetic daily
flow series.  Actual daily energy generation — accounting for pondage dispatch,
ecological flow constraints, and spillage — is used directly; no analytical
approximation is applied.

NPV is then computed for each loan interest rate $r_\ell \in [0\%, 10\%]$ and
both CAPEX scenarios.

```{r fff-compute}
#| cache: true

# Expected computation time (sequential):
#   N_SIM = 20,  3 CV levels  →  60 sims   ~10-30 sec
#   N_SIM = 200, 7 CV levels  →  1400 sims ~3-5 min
# Progress printed every 20 rows.

run_fff <- function(capex, label) {
  run_fff_grid(
    grid_df         = climate$grid_df,
    r_loan_seq      = R_LOAN_SEQ,
    ltv             = LTV,
    r_equity        = R_EQUITY,
    e_flow_mode     = E_FLOW_MODE,
    capex_ntd       = capex,
    opex_ntd_yr     = capex * OPEX_RATE,
    project_life_yr = PROJECT_LIFE,
    fit_ntd_per_kwh = PPA,          # using PPA rate
    scale_w2        = TRUE
  ) |>
  # Fix facet label: "run_of_river" → "Run-of-river", "pondage" → "Pondage"
  mutate(
    mode = recode(mode,
                  "run_of_river" = "Run-of-river",
                  "pondage"      = "Pondage"),
    capex_label = label
  )
}

message("FFF — CAPEX OG (5.0B)")
fff_og   <- run_fff(CAPEX_OG,   "CAPEX OG (5.0B)")

message("FFF — CAPEX EIA (6.4B)")
fff_eia  <- run_fff(CAPEX_EIA,  "CAPEX EIA (6.4B)")

message("FFF — CAPEX 2025 (9.7B)")
fff_2025 <- run_fff(CAPEX_2025, "CAPEX 2025 (9.7B)")

# Summarise each scenario
fff_og_sum   <- summarise_fff_grid(fff_og)   |> mutate(capex = "OG (5.0B)")
fff_eia_sum  <- summarise_fff_grid(fff_eia)  |> mutate(capex = "EIA (6.4B)")
fff_2025_sum <- summarise_fff_grid(fff_2025) |> mutate(capex = "2025 (9.7B)")
```

## NPV Results Table

```{r fff-table}
#| tbl-cap: "Median NPV (NTD billion) and P(NPV > 0) across bootstrap replicates. Pondage mode; CAPEX = NTD 9.7B; PPA = NTD 6.0/kWh. Format: NPV (viability %)."

fff_2025_sum |>
  filter(mode == "pondage") |>
  mutate(
    r_label = paste0(sprintf("%.0f", r_loan_pct), "%"),
    cell    = sprintf("%.2f (%.0f%%)", npv_P50, prob_viable * 100)
  ) |>
  select(cv_level, r_label, cell) |>
  tidyr::pivot_wider(
    names_from  = r_label,
    values_from = cell
  ) |>
  arrange(cv_level) |>
  rename(`CV level` = cv_level) |>
  knitr::kable(align = paste0("r", strrep("r", length(R_LOAN_SEQ))))
```

## FFF Heatmap — CAPEX OG (NTD 5.0B)

```{r fff-og}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "FFF — CAPEX = NTD 5.0B (earliest public announcement). PPA = NTD 6.0/kWh."

plot_fff_mode_comparison(
  fff_og_sum,
  title_text = "FFF: Run-of-river vs Pondage  |  CAPEX = NTD 5.0B (OG announcement)"
)
```

## FFF Heatmap — CAPEX EIA (NTD 6.4B)

```{r fff-eia}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "FFF — CAPEX = NTD 6.4B (1999 EIA feasibility report). PPA = NTD 6.0/kWh."

plot_fff_mode_comparison(
  fff_eia_sum,
  title_text = "FFF: Run-of-river vs Pondage  |  CAPEX = NTD 6.4B (EIA 1999)"
)
```

## FFF Heatmap — CAPEX 2025 (NTD 9.7B)

```{r fff-2025}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "FFF — CAPEX = NTD 9.7B (2025 updated estimate). The updated CAPEX substantially shifts the feasibility boundary, reducing the viable parameter space. PPA = NTD 6.0/kWh."

plot_fff_mode_comparison(
  fff_2025_sum,
  title_text = "FFF: Run-of-river vs Pondage  |  CAPEX = NTD 9.7B (2025 updated)"
)
```

## Pondage Advantage — Difference in P(NPV > 0)

```{r fff-diff}
#| fig-width: 9
#| fig-height: 4
#| fig-cap: "Difference in P(NPV > 0) between pondage and run-of-river operation. Positive values (green) indicate pondage has a higher probability of financial viability."

# Note: after recode() in fff-compute, mode values are "Pondage" and
# "Run-of-river" (title-case with hyphen).  pivot_wider creates columns
# with those exact names, so backtick-quote them in mutate().
diff_df <- fff_2025_sum |>
  select(cv_level, r_loan_pct, mode, prob_viable) |>
  tidyr::pivot_wider(names_from = mode, values_from = prob_viable) |>
  mutate(delta_prob = Pondage - `Run-of-river`)

ggplot(diff_df, aes(x = r_loan_pct, y = cv_level, fill = delta_prob)) +
  geom_tile(colour = "white", linewidth = 0.25) +
  geom_contour(aes(z = delta_prob), breaks = 0,
               colour = "black", linewidth = 0.8, linetype = "dashed") +
  scale_fill_gradient2(
    low      = "#D85A30",
    mid      = "#F5F5F0",
    high     = "#1D9E75",
    midpoint = 0,
    labels   = scales::percent,
    name     = expression(Delta * "P(NPV>0)")
  ) +
  scale_x_continuous(labels = function(x) paste0(x, "%"),
                     breaks = R_LOAN_SEQ * 100) +
  scale_y_continuous(breaks = CV_GRID_USE) +
  labs(
    title    = "Pondage Advantage over Run-of-River",
    subtitle = expression(
      "Difference in P(NPV>0): " * Delta == P[Pondage] - P["Run-of-river"]),
    x        = "Loan interest rate (%)",
    y        = "Within-year flow CV",
    caption  = paste0(
      "CAPEX = NTD 9.7B; LTV = ", LTV * 100, "%; equity rate = ",
      R_EQUITY * 100, "%; project life = ", PROJECT_LIFE, " yr.",
      "\nPositive delta: pondage achieves higher probability of financial viability."
    )
  ) +
  theme_fengping() +
  theme(panel.grid = element_blank(), legend.position = "right")
```

---

# Summary and Policy Implications

```{r summary-table}
#| tbl-cap: "Summary of key results. Viability defined as P(NPV > 0) >= 0.50 (Pondage mode, r_loan = 3%). Revenue at PPA rate (NTD 6.0/kWh)."

extract_viability <- function(summ_df, capex_label) {
  summ_df |>
    filter(mode == "Pondage", abs(r_loan_pct - 3) < 0.01) |>
    select(cv_level, prob_viable, npv_P50, gwh_P50) |>
    mutate(capex = capex_label)
}

bind_rows(
  extract_viability(fff_og_sum,   "NTD 5.0B (OG)"),
  extract_viability(fff_eia_sum,  "NTD 6.4B (EIA)"),
  extract_viability(fff_2025_sum, "NTD 9.7B (2025)")
) |>
  mutate(
    viable_flag = if_else(prob_viable >= 0.5, "Yes", "No"),
    CV_label    = paste0("CV = ", cv_level)
  ) |>
  select(
    CAPEX               = capex,
    `CV level`          = CV_label,
    `P(NPV>0)`          = prob_viable,
    `Median NPV (NTD B)`= npv_P50,
    `Median GWh/yr`     = gwh_P50,
    `Viable?`           = viable_flag
  ) |>
  knitr::kable(digits = c(0, 0, 2, 2, 1, 0))
```

The Financial Feasibility Frontier reveals that:

1. **Pondage consistently outperforms run-of-river** across all CV levels and
   loan rates, confirming that even the small pondage capacity of W1 and W2
   provides measurable financial value through improved dispatch flexibility.

2. **The updated CAPEX (NTD 9.7B) substantially narrows the viable parameter
   space** relative to the original EIA estimate (NTD 6.4B).  Under current
   FIT rates and recommended ecological flow constraints, viability at the
   historical CV range (1.5–2.5) requires loan rates below approximately 3–4%.

3. **Higher hydrological variability (CV > 2.5) reduces viability**, because
   increased flashiness causes more frequent spill events that the small
   pondage cannot buffer, depressing effective annual generation.  This effect
   is captured only by the full reservoir simulation; a naive flow-based
   energy estimate would miss this mechanism.

4. **Under SSP5-8.5 projections (CV ≈ 3.0–4.0)**, even the pondage mode
   under the EIA CAPEX shows P(NPV > 0) < 0.50 at loan rates above 4–5%,
   suggesting that climate change materially increases financial risk beyond
   what a static feasibility study would capture.

```{r teardown}
#| cache: false
# Analysis complete.
message("fp_hydro_main.qmd render complete.")
```
